### 2015-04-18 implementation-packages.tex

\subsection{Packages}

@@

In Spack, packages are Python scripts that build software artifacts.  
Each package is a class that extends a generic {\tt Package}
base class.  {\tt Package} implements the bulk of the build process, but
subclasses provide their own {\tt install()} method to handle the
specifics of particular packages. Additionally,
Spack implements an embedded domain-specific language (DSL).  It provides
special directives such as {\tt depends\_on} and {\tt version} that add
metadata to the package class.

>>>>

\subsection{Packages}\label{sec:packages}

@@

In Spack, packages are Python scripts that build software artifacts.  
Each package is a class that extends a generic {\tt Package}
base class.  {\tt Package} implements the bulk of the build process, but
subclasses provide their own {\tt install} method to handle the
specifics of particular packages. The subclass does {\it not} have to
handle managing the install location.  Rather, Spack passes the {\tt install}
method a {\tt prefix} parameter.  The package implementor must ensure that
her {\tt install} function installs the package {\it into} the {\tt prefix},
but Spack ensures that {\tt prefix} is computed in such a way that it is
unique for every configuration of a package.  To further simplify 
package implementation, Spack implements an embedded domain-specific
language (DSL).  The DSL provides special directives such as {\tt depends\_on},
{\tt version}, {\tt provides}, and {\tt patch} that add metadata
to the package class.
